%++++++++++++++++++++++++++++++++++++++++
% Don't modify this section unless you know what you're doing!
\documentclass[letterpaper,12pt]{article}
%\usepackage{dutchcal}
\usepackage{boondox-cal}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}
%++++++++++++++++++++++++++++++++++++++++


\begin{document}

\title{Some Title}
\author{A. Uthor, C. Ontributor}
\date{\today}
\maketitle

\begin{abstract}
Doing cool stuff to find cooler stuff
\end{abstract}


\section{Introduction}

The very important physical effect has applications to something in the world. 

Formatting stuff to consider:
\begin{enumerate}
\item Do we want to use $\partial$-notation or $\dot{A}^{'}$-notation?
\item Do we want to be reminded what variables are fcns off (eg $\mathcal{b}(t,z)$) or is that too messy?
\item Do we want to use $h_{12}$ or $h_{\times}$? 
\item I am mixing between [t,x,y,z] and [0,1,2,3] which is maybe confusing? (ex. $\mathcal{E}_x$ vs $\mathcal{u}_1$)
\end{enumerate}


\section{Background}

Gravitational theories and the Gertsenshtein effect combined in groundbreaking ways.
We use a (1,-1,-1,-1) metric.

The paper used the Einstein-Maxwell Lagrangian
\begin{equation}
\mathcal{L}=\sqrt{g}(R+\kappa F_{\mu \nu}F^{\mu \nu}),
\end{equation}
where $g$ is the determinant of the metric, $R$ is the Ricci Scalar, and $F$ is the electromagnetic field tensor. 

Linearizing the action and varying it gives the Maxwell field equations and the linearized gravitational wave eqaution. Using a transverse traceless Lorentz gauge for $h$, a small metric perturbation, with $\mathcal{h}_{\mu \nu}=\mathcal{h}_{\mu \nu}(t,z)$, they evaluated the components of the field equations (making assumptions about the EM wave and background), giving two mixing equations:
\begin{equation}
\ddot{ \mathcal{b}}_y - \mathcal{b}_y^{''}=B_0\mathcal{h}^{''}_{12}
\end{equation}
\begin{equation}
\ddot{ \mathcal{h}}_{12} - \mathcal{h}^{''}_{12}=4B_0 \mathcal{b}_y
\end{equation}

Here, we have a background magnetic field $\mathbf{B_0}=\mathbf{B}_{0x}$, and a magnetic perturbation $\mathbf{b}=\mathbf{b}_y (t,z)$. We have no electric field in the background, only in the wave.

We recreated the calculation with torsion, and got back the same equations.
\section{Our stuff}

We see what we get for the mixing equations with more complicated couplings in the lagrangian, with a torsion theory. We have a perturbation on the torsion given by 
\begin{equation}
\mathcal{T}^{\mu}_{\nu \sigma}=\epsilon^{\mu}_{\nu \sigma \lambda} \mathcal{Q}^{\lambda}+\delta^{\mu}_{[\nu} \mathcal{U}^{}_{\sigma]}
\end{equation}
with
\begin{equation}
\mathcal{Q}_{\mu}=[\mathcal{q}_0(t,z),0,\mathcal{q}_2(t,z),0]
\end{equation}
and
\begin{equation}
\mathcal{U}_{\mu}=[\mathcal{u}_0(t,z),0,\mathcal{u}_2(t,z),0].
\end{equation}

When we add inn a background torsion $T$, given by
\begin{equation}
T^{\mu}_{\nu \sigma}=\epsilon^{\mu}_{\nu \sigma \lambda}Q^{\lambda}
\end{equation}
with
\begin{equation}
Q_{\mu}=[q_0,0,0,0]
\end{equation}


\textbf{Lagrangian 1 - $R_{\mu \nu} F^{\mu \nu}$}
\begin{equation}
\mathcal{L}=\sqrt{g}(R+\zeta R_{\mu \nu} F^{\mu \nu}+\kappa F{\mu \nu}F^{\mu \nu})
\end{equation}

\underline{With no background torsion:}

Maxwell and Einstein gives us nothing new on the face of it. The torsion field equations give us a bunch of mixings (notably with only first-order derivatives):

\begin{equation}
\frac{1}{2}  B_0 \mathcal{h}_{11}^{'} -  \partial_{t}\mathcal{E}_y=0
\end{equation}

\begin{equation}
\frac{1}{2} B_0 \mathcal{u}_0 + \frac{1}{2} B_0 \dot{\mathcal{h}}_{11}-\partial_{y} \mathcal{E}_z=0
\end{equation}

\begin{equation}
\frac{1}{2} B_0 \dot{\mathcal{h}}_{12} - \dot{\mathcal{b}}_y=0
\end{equation}

We also have these three equations, which have some interesting impact on the original mixing equations we get from Maxwell and Einstein:
\begin{equation}
\frac{1}{2} B_0 \mathcal{h}_{12}^{'}-\mathcal{b}_y^{'}+\partial_t \mathcal{E}_x=0
\end{equation}

\begin{equation}
\frac{1}{2} B_0 \mathcal{h}_{12}^{'}-\mathcal{b}_y^{'}=0
\end{equation}

\begin{equation}
\frac{1}{2} B_0 \mathcal{h}_{12}^{'}+\partial_t \mathcal{E}_x=0
\end{equation}

meaning that each of the three terms individually are zero, removing the z-derivatives of both $\mathcal{h}_{\times}$ and $\mathcal{b}$ in our original mixing equations, leaving

\begin{equation}
\ddot{ \mathcal{b}}_y=0
\end{equation}
\begin{equation}
\ddot{ \mathcal{h}}_{12} =4B_0 \mathcal{b}_y
\end{equation}


This lagrangian does not allow for a finite background torsion.


\textbf{Lagrangian 2} - $\epsilon_{\mu \nu \sigma \lambda} R^{\mu \nu} F^{\sigma \lambda}$
\begin{equation}
\mathcal{L}=\sqrt{g}(R+\zeta \epsilon_{\mu \nu \sigma \lambda} R^{\mu \nu} F^{\sigma \lambda}+\kappa F{\mu \nu}F^{\mu \nu})
\end{equation}

\underline{With no background torsion:}

No change in Maxwell, Einstein gave same mixing equation. Torsion field eqs gave some equations though:
\begin{equation}
2 \mathcal{b}_y^{'}-B_0\mathcal{h}_{12}^{'}+B_0\mathcal{q}_0=0
\end{equation}

\begin{equation}
-B_0\dot{\mathcal{h}}_{11}+2\partial_z\mathcal{E}_y=0
\end{equation}

\begin{equation}
-2 \dot{\mathcal{b}}_y-B_0\dot{\mathcal{h}}_{12}+2\partial_z\mathcal{E}_x=0
\end{equation}

\begin{equation}
B_0\dot{\mathcal{h}}_{12}-2\partial_z\mathcal{E}_x+2\partial_x\mathcal{E}_z=0
\end{equation}

Here, the two last equations give us
\begin{equation}
-2 \dot{\mathcal{b}}_y-B_0\dot{\mathcal{h}}_{12}=0
\end{equation}
with
\begin{equation}
2\partial_z\mathcal{E}_x=0
\end{equation}
since
\begin{equation}
-\partial_z\mathcal{E}_x+\partial_x\mathcal{E}_z=\dot{\mathcal{b}}_y
\end{equation}
meaning that in this case,
\begin{equation}
\partial_x\mathcal{E}_z=\dot{\mathcal{b}}_y
\end{equation}
which might be worth noting for further calculations, but has no immediate effect.


\underline{With background torsion:}
Not started.



\textbf{Lagrangian 3 - $R_{\mu \nu} R^{\mu \nu}$}
\begin{equation}
\mathcal{L}=\sqrt{g}(R+\zeta R_{\mu \nu} R^{\mu \nu}+\kappa F{\mu \nu}F^{\mu \nu})=0
\end{equation}

\underline{With no background torsion:}

The torsion field equations have no EM-components, and only serve to help us simplify the other equations.
The maxwell field equations are unchanged. 

For the Einstein equation we get some higher-order derivatives, but no torsion contribution:

\begin{equation}
-4 \kappa B_0 \mathcal{b}_y-\mathcal{h}_{12}^{''}+\ddot{\mathcal{h}}_{12}+\zeta \mathcal{h}^{''''}_{12}+2  \zeta \ddot{\mathcal{h}}_{12}^{''}+\zeta \ddddot{\mathcal{h}}_{12}=0
\end{equation}


\underline{With background torsion:} Not finsihed running.


We also did a run with the indices on the second Ricci tensor swapped, but achieved the same mixing equations (different torsion field equations, but that had no effect on the mixing equations).


\textbf{Lagrangian 4} - $ R_{\mu \nu \sigma \lambda} R^{\mu \nu \sigma \lambda}$
\begin{equation}
\mathcal{L}=\sqrt{g}(R+\zeta R_{\mu \nu \sigma \lambda} R^{\mu \nu \sigma \lambda}+\kappa F{\mu \nu}F^{\mu \nu})
\end{equation}

\underline{With no background torsion:}

Maxwell still gives the same equations as expected.

Torsion still only gives some substitutions

Einstein is not done evaluating.



\underline{With background torsion:}
Not started

\textbf{Lagrangian 5} - $ R_{\mu \nu \sigma \lambda} R^{\mu \sigma \nu \lambda}$
Not finished running

\textbf{Lagrangian 6} - $ R_{\mu \nu \sigma \lambda} R^{\sigma \lambda \mu \nu }$
Not finished running

\section{Conclusions}
The world is forever changed

%++++++++++++++++++++++++++++++++++++++++
% References section will be created automatically 
% with inclusion of "thebibliography" environment
% as it shown below. See text starting with line
% \begin{thebibliography}{99}
% Note: with this approach it is YOUR responsibility to put them in order
% of appearance.

\begin{thebibliography}{99}

\bibitem{bib} \emph{A source},  available at
\texttt{https://wevbarker.com/}.

\end{thebibliography}


\end{document}