%MacrosJournalNames

% Journal names 
\def\aj{\rm{AJ}}
\def\actaa{\rm{Acta Astron.}}
\def\araa{\rm{ARA\&A}}
\def\apj{\rm{ApJ}}
\def\apjl{\rm{ApJ}}
\def\apjs{\rm{ApJS}}
\def\ao{\rm{Appl.~Opt.}}
\def\apss{\rm{Ap\&SS}}
\def\aap{\rm{A\&A}}
\def\aapr{\rm{A\&A~Rev.}}
\def\aaps{\rm{A\&AS}}
\def\azh{\rm{AZh}}
\def\baas{\rm{BAAS}}
\def\bac{\rm{Bull. astr. Inst. Czechosl.}}
\def\caa{\rm{Chinese Astron. Astrophys.}}
\def\cjaa{\rm{Chinese J. Astron. Astrophys.}}
\def\icarus{\rm{Icarus}}
\def\jcap{\rm{J. Cosmology Astropart. Phys.}}
\def\jrasc{\rm{JRASC}}
\def\memras{\rm{MmRAS}}
\def\mnras{\rm{MNRAS}}
\def\na{\rm{New A}}
\def\nar{\rm{New A Rev.}}
\def\pra{\rm{Phys.~Rev.~A}}
\def\prb{\rm{Phys.~Rev.~B}}
\def\prc{\rm{Phys.~Rev.~C}}
\def\prd{\rm{Phys.~Rev.~D}}
\def\pre{\rm{Phys.~Rev.~E}}
\def\prl{\rm{Phys.~Rev.~Lett.}}
\def\pasa{\rm{PASA}}
\def\pasp{\rm{PASP}}
\def\pasj{\rm{PASJ}}
\def\rmxaa{\rm{Rev. Mexicana Astron. Astrofis.}}
\def\qjras{\rm{QJRAS}}
\def\skytel{\rm{S\&T}}
\def\solphys{\rm{Sol.~Phys.}}
\def\sovast{\rm{Soviet~Ast.}}
\def\ssr{\rm{Space~Sci.~Rev.}}
\def\zap{\rm{ZAp}}
\def\nat{\rm{Nature}}
\def\iaucirc{\rm{IAU~Circ.}}
\def\aplett{\rm{Astrophys.~Lett.}}
\def\astropj{\rm{Astrophys.~J.}}
\def\apspr{\rm{Astrophys.~Space~Phys.~Res.}}
\def\bain{\rm{Bull.~Astron.~Inst.~Netherlands}}
\def\fcp{\rm{Fund.~Cosmic~Phys.}}
\def\gca{\rm{Geochim.~Cosmochim.~Acta}}
\def\grl{\rm{Geophys.~Res.~Lett.}}
\def\jcp{\rm{J.~Chem.~Phys.}}
\def\jgr{\rm{J.~Geophys.~Res.}}
\def\jqsrt{\rm{J.~Quant.~Spec.~Radiat.~Transf.}}
\def\memsai{\rm{Mem.~Soc.~Astron.~Italiana}}
\def\nphysa{\rm{Nucl.~Phys.~A}}
\def\nphys{\rm{Nucl.~Phys.}}
\def\physrep{\rm{Phys.~Rep.}}
\def\physscr{\rm{Phys.~Scr}}
\def\planss{\rm{Planet.~Space~Sci.}}
\def\procspie{\rm{Proc.~SPIE}}
\def\procrsa{\rm{Proc.~Math.~Phys.~Eng.~Sci.}}
\def\annmath{\rm{Ann.~Math.}}
\def\mathann{\rm{Math.~Ann.}}
\def\annphys{\rm{Ann.~Physics (N.~Y.)}}
\def\annderphys{\rm{Ann.~Phys.}}
\def\ptrsla{\rm{Philos.~Trans.~R.~Soc~A}}
\def\ptrslo{\rm{Philos.~Trans.~R.~Soc~I}}
\def\jmp{\rm{J.~Math.~Phys.}}
\def\cqg{\rm{Class.~Quantum~Gravity}}
\def\physrev{\rm{Phys.~Rev.}}
\def\foundphys{\rm{Found.~Phys.}}
\def\epjc{\rm{Eur.~Phys.~J.~C}}
\def\natast{\rm{Nat.~Astron.}}
\def\pdu{\rm{Phys.~Dark~Universe}}
\def\araa{\rm{Annu.~Rev.~Astron.~Astrophys.}}
\def\nrp{\rm{Nat.~Rev.~Phys.}}
\def\rpp{\rm{Rep.~Prog.~Phys.}}
\def\ijmpd{\rm{Int.~J.~Mod.~Phys.~D}}
\def\pletta{\rm{Phys.~Lett.~A}}
\def\plettb{\rm{Phys.~Lett.~B}}
\def\grg{\rm{Gen.~Relativ.~Gravit.}}
\def\phyrep{\rm{Phys.~Rep.}}
\def\jhep{\rm{J.~High~Energy~Phys.}}
\def\rmphy{\rm{Rev.~Mod.~Phys.~D}}
\def\rmphyo{\rm{Rev.~Mod.~Phys}}
\def\fass{\rm{Front.~Astron.~Space~Sci.}}
\def\progtp{\rm{Prog.~Theor.~Phys.}}
\def\appb{\rm{Acta~Phys.~Pol.~B}}
\def\crphys{\rm{C.~R.~Phys.}}
\def\ijtp{\rm{Int.~J.~Theor.~Phys.}}
\def\progpnp{\rm{Prog.~Part.~Nucl.~Phys.}}
\def\nucphyb{\rm{Nucl.~Phys.~B}}
\def\npcs{\rm{Nonlin.~Phenom.~Complex~Syst.}}
\def\nar{\rm{New.~Astron.~Rev.}}
\def\cjp{\rm{Chin.~J.~Phys.}}
\def\ujp{\rm{Ukr.~J.~Phys.}}
\def\aaca{\rm{Adv.~Appl.~Clifford~Algebras}}
\def\sjetpl{\rm{Sov.~JETP~Lett.}}
\def\mathz{\rm{Math.~Z.}}
\def\macsp{\rm{Mem.~Acad.~St.~Petersbourg}}
\def\rprogphy{\rm{Rept.~Prog.~Phys.}}
\def\annhp{\rm{Ann.~Henri~Poincar\'e}}%Annales de l'I.H.P. Physique th\'eorique
\def\astronj{\rm{Astron.~J.}}
\def\ijgmmp{\rm{Int.~J.~Geom.~Meth.~Mod.~Phys.}}
\def\pispf{\rm{Proc.~Int.~Sch.~Phys.~Fermi}}
\def\livrevrel{\rm{Living~Rev.~Relativ.}}
